---
title: "Obesity Level Predictive Modeling"
author: "Zachary Cannon, Makayla Harvey, Giancarlo Pantano, Kaylen Ton, Megan Xiao"
output:
  word_document: default
  html_document:
    df_print: paged
---

### Load packages

```{r - packages and data}

library(tidyverse)
library(tidymodels)
library(vip)
library(ggplot2)

# For parallel processing when it comes to tuning multiple models (which can take longer)
library(parallelly)
library(future)
cores <- availableCores(logical = F)
plan(multisession, workers = cores)

```

### Load in and separate normal and synthetic data

```{r}

# Load raw data 

raw_data <- read.csv("ObesityData.csv", 
                     stringsAsFactors = FALSE)

cat("Number of rows:", nrow(raw_data),"\n",
    "Number of columns:", ncol(raw_data), "\n\n")
str(raw_data)
head(raw_data)

# Save a copy of raw_data with the duplicates for now
df <- raw_data

#Create DF with only real data
problem_cols <- c("Age","FCVC","NCP","CH2O","FAF","TUE")

is_decimal <- function(x){
  !is.na(x) & (x %% 1 != 0)
}

is_not_decimal <- function(x){
  !is.na(x) & (x %% 1 == 0)
}

#if at least one record in problem_cols is a decimal value, save in syn_df
syn_df <- df %>%
  filter(if_any(all_of(problem_cols), is_decimal))
nrow(syn_df)

#if all records in problem_cols are whole numbers, save in normal_df
normal_df <- df %>%
  filter(if_all(all_of(problem_cols), is_not_decimal))
nrow(normal_df)

#ensure rows add to 2111
nrow(syn_df) + nrow(normal_df)
```

### EDA: Comparing NObeyesdad between Synthetic data, Real data, and All data

```{r}
#histogram of normal_df NObeyesdad
norm_df_count <- normal_df %>%
  count(NObeyesdad) %>%
  arrange(desc(n))

p <- ggplot(norm_df_count, aes(x= NObeyesdad, y = n, fill = NObeyesdad)) +
  geom_col() +
  labs(title = "Counts of Obesity Levels (Normal/Real Data only)",
       x = "Obesity Level",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
p
#most are of "Normal Weight"

syn_df_count <- syn_df %>%
  count(NObeyesdad) %>%
  arrange(desc(n))

p2 <- ggplot(syn_df_count, aes(x=NObeyesdad, y = n, fill = NObeyesdad)) +
  geom_col() +
  labs(title = "Counts of Obesity Levels (Synthetic Data only)",
       x = "Obesity Level",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
p2
#classes are balanced, but no "Normal Weight"

df_count <- df %>%
  count(NObeyesdad) %>%
  arrange(desc(n))

p3 <- ggplot(df_count, aes(x=NObeyesdad, y=n, fill=NObeyesdad))+
  geom_col() +
  labs(title = "Counts of Obesity Levels (All Rows - Normal/Read + Synthetic)",
       x = "Obesity Level",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
p3
#"Normal Weight" is as balanced as the other classes when we consider all NObeyesdad values
```

## Cleaning Data: Rounding
```{r}
#Because syn_df does not contain "Normal Weight", we will not use it for model training. We will instead compare model training results with normal_df (contains only real data) and df (contains BOTH real and synthetic data)

# Rounding Logic for both normal_df and df:
str(df)
#   Age     0 decimals, age in years, whole number only
#   Height  2 decimals height in meters, 2 decimal points for cm precision
#   Weight  1 decimal weight in kg, 1 decimal point is sufficient
#   FCVC    0 decimals scale 1-3, whole number only (categorical) - recoded to 0/1/2 for consistency
#   NCP     0 decimals number of meals, whole number only
#   CH2O    0 decimal water intake scale 1-3, whole number only (in liters) - recoded to 0/1/2 for consistency
#   FAF     0 decimal physical activity scale 0-3 (in days)
#   TUE     0 decimals tech use scale 0-2, whole number only

#Rounding code:
round_df <- function(df){
  df$Age    <- round(df$Age,    0)
  df$Height <- round(df$Height, 2)
  df$Weight <- round(df$Weight, 1)
  df$FCVC   <- as.numeric(round(df$FCVC, 0))
  #Recode FCVC to 0/1/2
  df$FCVC <- df$FCVC - 1
  df$NCP    <- as.numeric(round(df$NCP,  0))
  df$CH2O   <- round(df$CH2O, 0)
  #Recode CH2O to 0/1/2
  df$CH2O <- df$CH2O - 1
  df$FAF    <- round(df$FAF,  0)
  df$TUE    <- as.numeric(round(df$TUE,  0))
  
  return(df)
}

normal_df <- round_df(normal_df)
df <- round_df(df)

#Convert NObeyesdad to factors
normal_df$NObeyesdad <- as.factor(normal_df$NObeyesdad)
df$NObeyesdad <- as.factor(df$NObeyesdad)
```

# **Modeling**

## Splitting Data

```{r}

# Set seed for reproducibility 
set.seed(73)

# Split data
normal_df_split <- initial_split(normal_df, strata = NObeyesdad)
syn_df_split <- initial_split(df, strata = NObeyesdad)

normal_obesity_train <- training(normal_df_split)
normal_obesity_test <- testing(normal_df_split)

syn_obesity_train <- training(syn_df_split)
syn_obesity_test <- testing(syn_df_split)

# Preparing folds for cross validation and resampling
normal_tree_folds <- vfold_cv(normal_obesity_train, v = 10,
                       strata = NObeyesdad)
syn_tree_folds <- vfold_cv(syn_obesity_train, v = 10,
                           strata = NObeyesdad)
    
# Creating custom metrics
tree_metrics <- metric_set(accuracy, roc_auc, sens, spec)

```


# Model 1 - Base Decision Tree: Real Data (normal_df)

```{r}

### REAL DATA (normal_df) ###

# Specify Model
base_tree_model <- decision_tree() %>% 
  set_engine('rpart') %>% 
  set_mode('classification')

# Create Recipe
tree_recipe <- recipe(NObeyesdad ~ ., data = normal_obesity_train) %>%
  step_novel(all_nominal_predictors(), new_level = "other") %>% 
  step_dummy(all_nominal_predictors())

# Create Workflow
tree_workflow <- workflow() %>% 
  add_model(base_tree_model) %>% 
  add_recipe(tree_recipe)

# Fit resamples (CV)
tree_fit_resample <- tree_workflow %>%
  fit_resamples(resamples = normal_tree_folds,
                metrics = tree_metrics)
    
tree_fit_rs_result <- tree_fit_resample %>% 
  collect_metrics(summarize = F)

tree_fit_rs_result %>%
  filter(.metric == 'roc_auc') %>% 
  group_by(id) %>%
  summarize(min_roc_auc = min(.estimate),
            median_roc_auc = median(.estimate),
            max_roc_auc = max(.estimate))

tree_fit_rs_result %>%
  group_by(.metric) %>%
  summarize(min = min(.estimate),
            median = median(.estimate),
            max = max(.estimate))

# 10 fold estimates (CV results)
#   .metric       min         median        max
#   accuracy	  0.6052632	  0.7434211	  0.8000000	
#   roc_auc	    0.7821145	  0.8875162	  0.9562112	
#   sens	      0.4085859	  0.5702521	  0.7759420	
#   spec	      0.9119484	  0.9459625	  0.9598066

# obtain mean roc_auc score
tree_fit_rs_result %>%
  filter(.metric == "roc_auc") %>%
  group_by(.metric) %>%
  summarize(mean = mean(.estimate))

# .metric     .mean
#   roc_auc	0.8848726

# Fit & Test
base_tree_fit <- tree_workflow %>% 
  last_fit(split = normal_df_split, metrics = tree_metrics)

# Collect Metrics    
base_tree_fit %>% 
  collect_metrics()

# Base decision tree model results
# accuracy	multiclass	0.7984496
# sens	    macro	      0.6822979	
# spec	    macro	      0.9561176	
# roc_auc	  hand_till	  0.9388945	
```

# Model 1 - Base Decision Tree: Synthetic data (df)

```{r}

tree_recipe <- recipe(NObeyesdad ~ ., data = syn_obesity_train) %>%
  step_novel(all_nominal_predictors(), new_level = "other") %>% 
  step_dummy(all_nominal_predictors())

# Create Workflow
tree_workflow <- workflow() %>% 
  add_model(base_tree_model) %>% 
  add_recipe(tree_recipe)

# Fit resamples (CV)
tree_fit_resample <- tree_workflow %>%
  fit_resamples(resamples = syn_tree_folds,
                metrics = tree_metrics)
    
tree_fit_rs_result <- tree_fit_resample %>% 
  collect_metrics(summarize = F)

tree_fit_rs_result %>%
  filter(.metric == 'roc_auc') %>% 
  group_by(id) %>%
  summarize(min_roc_auc = min(.estimate),
            median_roc_auc = median(.estimate),
            max_roc_auc = max(.estimate))

tree_fit_rs_result %>%
  group_by(.metric) %>%
  summarize(min = min(.estimate),
            median = median(.estimate),
            max = max(.estimate))

# 10 fold estimates (CV results)
#   .metric       min         median        max
#   accuracy	  0.8456790	  0.8846106	  0.9096774	
#   roc_auc	    0.9655698	  0.9761792	  0.9860841	
#   sens	      0.8438571	  0.8783675	  0.9086866	
#   spec	      0.9742624	  0.9808544	  0.9850412	

# obtain mean roc_auc score
tree_fit_rs_result %>%
  filter(.metric == "roc_auc") %>%
  group_by(.metric) %>%
  summarize(mean = mean(.estimate))

# .metric     .mean
#   roc_auc	  0.97596	

# Fit & Test
base_tree_fit <- tree_workflow %>% 
  last_fit(split = syn_df_split, metrics = tree_metrics)

# Collect Metrics    
base_tree_fit %>% 
  collect_metrics()

# Base decision tree model results
# accuracy	multiclass	0.8849057	
# sens	    macro	      0.8809348	
# spec	    macro	      0.9808438		
# roc_auc	  hand_till	  0.9776858	

```


# Model 2 - Base Decision Tree Model w/ Tuned Hyper-Parameters: Real Data (normal_df)

```{r}

# Specify Model
tune_tree_model <- decision_tree(
  cost_complexity = tune(),
  tree_depth = tune(),
  min_n = tune()
  ) %>% 
  set_engine('rpart') %>% 
  set_mode('classification')

# Create tuning grid for hyper-parameters
tree_grid <- grid_random(extract_parameter_set_dials(tune_tree_model), size = 20)

# Update workflow object with new model: tune_tree_model
tree_workflow <- tree_workflow %>%
  update_model(tune_tree_model)

# Tuning and resampling (cv)
tuning_tree_results <- tree_workflow %>% 
  tune_grid(resamples = normal_tree_folds,
            grid = tree_grid,
            metrics = tree_metrics)

tuning_tree_results %>% 
  collect_metrics(summarize = FALSE) %>% 
  filter(.metric == "roc_auc") %>% 
  group_by(id) %>% 
  summarize(min_roc_auc = min(.estimate),
            median_roc_auc = median(.estimate),
            max_roc_auc = max(.estimate))

autoplot(tuning_tree_results)

tuning_tree_results %>% 
  show_best(metric = 'roc_auc', n = 5)

# Top 5:
# cost_complexity     tree_depth    min_n   .metric   .estimator    mean          n     std_err
# 3.243197e-04	      15	          20	    roc_auc	  hand_till	    0.9016376	    10	  0.01725857
# 1.258728e-04	      9	            21	    roc_auc	  hand_till	    0.8996373	    10	  0.01683664
# 1.102454e-02	      11	          14	    roc_auc	  hand_till	    0.8945377	    10	  0.02182977
# 8.593975e-09	      7	            18	    roc_auc	  hand_till	    0.8898451	    10	  0.02039882
# 2.018634e-04	      7	            18	    roc_auc	  hand_till	    0.8898451	    10	  0.02039882	

# obtain mean roc_auc score
tuning_tree_results %>%
  show_best(metric = "roc_auc") %>%
  group_by(.metric) %>%
  summarize(mean = mean(mean))
# .metric   .mean
# roc_auc  0.8951006		

best_tune_tree_model <- tuning_tree_results %>% 
  select_best(metric = 'roc_auc')

final_tune_tree_workflow <- tree_workflow %>% 
  finalize_workflow(best_tune_tree_model)

final_tune_tree_fit <- final_tune_tree_workflow %>% 
  last_fit(split = normal_df_split, metrics = tree_metrics)

final_tune_tree_fit %>% 
  collect_metrics()

# Tuned Decision Tree Model Results
# accuracy multiclass     0.7984496 
# sens     macro          0.7379486 
# spec     macro          0.9602287
# roc_auc  hand_till      0.9381596 

```
# Model 2 - Base Decision Tree Model w/ Tuned Hyper-Parameters: Synthetic Data (df)

```{r}

# Specify Model
tune_tree_model <- decision_tree(
  cost_complexity = tune(),
  tree_depth = tune(),
  min_n = tune()
  ) %>% 
  set_engine('rpart') %>% 
  set_mode('classification')

# Create tuning grid for hyper-parameters
tree_grid <- grid_random(extract_parameter_set_dials(tune_tree_model), size = 20)

# Update workflow object with new model: tune_tree_model
tree_workflow <- tree_workflow %>%
  update_model(tune_tree_model)

# Tuning and resampling (cv)
tuning_tree_results <- tree_workflow %>% 
  tune_grid(resamples = syn_tree_folds,
            grid = tree_grid,
            metrics = tree_metrics)

tuning_tree_results %>% 
  collect_metrics(summarize = FALSE) %>% 
  filter(.metric == "roc_auc") %>% 
  group_by(id) %>% 
  summarize(min_roc_auc = min(.estimate),
            median_roc_auc = median(.estimate),
            max_roc_auc = max(.estimate))

autoplot(tuning_tree_results)

tuning_tree_results %>% 
  show_best(metric = 'roc_auc', n = 5)

# Top 5:
# cost_complexity     tree_depth    min_n   .metric   .estimator    mean          n     std_err
# 1.360564e-05	      14	          22	    roc_auc	  hand_till	    0.9825882	    10	  0.002290333	
# 2.537619e-10	      10	          15	    roc_auc	  hand_till	    0.9823914	    10	  0.002352027	
# 2.994957e-06	      9	            35	    roc_auc	  hand_till	    0.9819036	    10	  0.001896366	
# 9.723147e-10	      8	            37	    roc_auc	  hand_till	    0.9818976	    10	  0.001896149
# 5.640532e-08	      7	            39	    roc_auc	  hand_till	    0.9803524	    10	  0.001934734

# obtain mean roc_auc score
tuning_tree_results %>%
  show_best(metric = "roc_auc") %>%
  group_by(.metric) %>%
  summarize(mean = mean(mean))

# .metric   .mean
# roc_auc  0.9818266	

best_tune_tree_model <- tuning_tree_results %>% 
  select_best(metric = 'roc_auc')

final_tune_tree_workflow <- tree_workflow %>% 
  finalize_workflow(best_tune_tree_model)

final_tune_tree_fit <- final_tune_tree_workflow %>% 
  last_fit(split = syn_df_split, metrics = tree_metrics)

final_tune_tree_fit %>% 
  collect_metrics()

# Tuned Decision Tree Model Results
# accuracy multiclass     0.9433962 
# sens     macro          0.9424962 
# spec     macro          0.9905704
# roc_auc  hand_till      0.9888267 

```

# Model 3.1 - Gradient Boosted Tree Model: Real Data (normal_df)

```{r}

# Specify Model
gradient_boost_tree_model <- boost_tree() %>% 
  set_mode("classification") %>% 
  set_engine("xgboost")

# Create Recipe
boost_recipe <- recipe(NObeyesdad ~ ., data = normal_obesity_train) %>%
  step_novel(all_nominal_predictors(), new_level = "other") %>% 
  step_dummy(all_nominal_predictors())

# Create Workflow
boost_workflow <- workflow() %>% 
  add_recipe(boost_recipe) %>% 
  add_model(gradient_boost_tree_model)

# Last fit - train and test
boosted_fit <- boost_workflow %>%
 last_fit(NObeyesdad ~ ., split = normal_df_split, metrics = tree_metrics)

boosted_fit %>% 
  collect_metrics()

# Base gradient boosted tree model results
  # accuracy multiclass     0.8372093 
  # sens     macro          0.6813674 
  # spec     macro          0.9597362
  # roc_auc  hand_till      0.9397156 

# Collect predictions
boosted_predictions <- boosted_fit %>% 
  collect_predictions()

boosted_predictions

boosted_predictions <- boosted_predictions %>%
  mutate(NObeyesdad = fct_drop(NObeyesdad))

# Visualize ROC curve
boosted_roc <- boosted_predictions %>% 
  roc_curve(truth = NObeyesdad, .pred_Insufficient_Weight:.pred_Overweight_Level_II,
            -.pred_Obesity_Type_III, #drop obesity type III since none exist in the test set
        estimator = "macro")

ggplot(boosted_roc, aes(x = 1 - specificity, y = sensitivity, color = .level)) +
  geom_line(linewidth = .75, alpha = .75) +
  labs(color = "Obesity Level") +
  geom_abline(lty = 2, alpha = .5) +
  theme_light() +
  labs(title = "ROC Curve 3: Gradient Boosted Tree Model (Real Data)")

```
# Model 3.1 - Gradient Boosted Tree Model: Synthetic Data (df)

```{r}
# Specify Model
gradient_boost_tree_model <- boost_tree() %>% 
  set_mode("classification") %>% 
  set_engine("xgboost")

# Create Recipe
boost_recipe <- recipe(NObeyesdad ~ ., data = syn_obesity_train) %>%
  step_novel(all_nominal_predictors(), new_level = "other") %>% 
  step_dummy(all_nominal_predictors())

# Create Workflow
boost_workflow <- workflow() %>% 
  add_recipe(boost_recipe) %>% 
  add_model(gradient_boost_tree_model)

# Last fit - train and test
boosted_fit <- boost_workflow %>%
 last_fit(NObeyesdad ~ ., split = syn_df_split, metrics = tree_metrics)

boosted_fit %>% 
  collect_metrics()

# Base gradient boosted tree model results
  # accuracy multiclass     0.9716981 
  # sens     macro          0.9702199 
  # spec     macro          0.9952840
  # roc_auc  hand_till      0.9977706 

# Collect predictions
boosted_predictions <- boosted_fit %>% 
  collect_predictions()

boosted_predictions


# Visualize ROC curve
boosted_roc <- boosted_predictions %>% 
  roc_curve(truth = NObeyesdad, .pred_Insufficient_Weight:.pred_Overweight_Level_II,
        estimator = "macro")

ggplot(boosted_roc, aes(x = 1 - specificity, y = sensitivity, color = .level)) +
  geom_line(linewidth = .75, alpha = .75) +
  labs(color = "Obesity Level") +
  geom_abline(lty = 2, alpha = .5) +
  theme_light() +
  labs(title = "ROC Curve 3: Gradient Boosted Tree Model (Synthetic Data)")
```


# Model 3.2 - Gradient Boosted Tree Model w/ Tuned Hyper-Parameters: Real Data (normal_df)

```{r}

# Gradient Boosted Tree w/ Tuning
tune_gradient_boost_tree_model <- boost_tree(
    trees = tune(),
    learn_rate = tune(),
    tree_depth = tune(),
    sample_size = tune()
  ) %>% 
  set_mode("classification") %>% 
  set_engine("xgboost")

# Create tuning grid for hyper-parameters
gradient_tree_grid <- grid_random(extract_parameter_set_dials(tune_gradient_boost_tree_model), size = 30)

# Update workflow object with new model: tune_gradient_boost_tree_model
tree_workflow <- tree_workflow %>%
  update_model(tune_gradient_boost_tree_model)

# Tuning and resampling (cv)
tuning_gradient_tree_results <- tree_workflow %>% 
  tune_grid(resamples = normal_tree_folds,
            grid = gradient_tree_grid,
            metrics = tree_metrics)

tuning_gradient_tree_results %>% 
  collect_metrics(summarize = FALSE) %>% 
  filter(.metric == "roc_auc") %>% 
  group_by(id) %>% 
  summarize(min_roc_auc = min(.estimate),
            median_roc_auc = median(.estimate),
            max_roc_auc = max(.estimate))

autoplot(tuning_gradient_tree_results)

tuning_gradient_tree_results %>% 
  show_best(metric = 'roc_auc', n = 5)

# Top 5:
# trees   tree_depth  learn_rate  sample_size   .metric   .estimator    mean        n     std_err
# 1871	  11	        0.013749865	0.7860675	    roc_auc	  hand_till	    0.9269546	  10	  0.009176586
# 898	    12	        0.003692208	0.8881136	    roc_auc	  hand_till	    0.9268193	  10	  0.011009459
# 457	    3	          0.028356323	0.7688713	    roc_auc	  hand_till	    0.9243418	  10	  0.009407939
# 1537	  14	        0.001700274	0.8570314	    roc_auc	  hand_till	    0.9230048	  10	  0.011836180	
# 936	    10	        0.002553602	0.7410630	    roc_auc	  hand_till	    0.9217199	  10	  0.012767880

# obtain mean roc_auc score
tuning_gradient_tree_results %>%
  show_best(metric = "roc_auc") %>%
  group_by(.metric) %>%
  summarize(mean = mean(mean))

# .metric   mean
# roc_auc	0.9296265		

best_tune_tree_model <- tuning_gradient_tree_results %>% 
  select_best(metric = 'roc_auc')

final_tune_tree_workflow <- tree_workflow %>% 
  finalize_workflow(best_tune_tree_model)

final_tune_tree_fit <- final_tune_tree_workflow %>% 
  last_fit(split = normal_df_split, metrics = tree_metrics)

final_tune_tree_fit %>% 
  collect_metrics()

# Tuned Gradient Boost Model Results
  # accuracy	    multiclass	  0.8372093
  # sens	        macro	        0.6825161
  # spec	        macro	        0.9610802
  # roc_auc	      hand_till	    0.9523730

```

# Model 3.2 - Gradient Boosted Tree Model w/ Tuned Hyper-Parameters: Synthetic Data (df)
```{r}
# Gradient Boosted Tree w/ Tuning
tune_gradient_boost_tree_model <- boost_tree(
    trees = tune(),
    learn_rate = tune(),
    tree_depth = tune(),
    sample_size = tune()
  ) %>% 
  set_mode("classification") %>% 
  set_engine("xgboost")

# Create tuning grid for hyper-parameters
gradient_tree_grid <- grid_random(extract_parameter_set_dials(tune_gradient_boost_tree_model), size = 30)

# Update workflow object with new model: tune_gradient_boost_tree_model
tree_workflow <- tree_workflow %>%
  update_model(tune_gradient_boost_tree_model)

# Tuning and resampling (cv)
tuning_gradient_tree_results <- tree_workflow %>% 
  tune_grid(resamples = syn_tree_folds,
            grid = gradient_tree_grid,
            metrics = tree_metrics)

tuning_gradient_tree_results %>% 
  collect_metrics(summarize = FALSE) %>% 
  filter(.metric == "roc_auc") %>% 
  group_by(id) %>% 
  summarize(min_roc_auc = min(.estimate),
            median_roc_auc = median(.estimate),
            max_roc_auc = max(.estimate))

autoplot(tuning_gradient_tree_results)

tuning_gradient_tree_results %>% 
  show_best(metric = 'roc_auc', n = 5)

# Top 5:
# trees   tree_depth  learn_rate  sample_size   .metric   .estimator    mean        n     std_err
# 1041	  6	          0.02855801	0.6350682	    roc_auc	  hand_till	    0.9988747	  10	  0.0002577269
# 1003	  6	          0.05915703	0.7647551	    roc_auc	  hand_till	    0.9988500	  10	  0.0002855007
# 655	    8	          0.25178004	0.9765933	    roc_auc	  hand_till	    0.9988047	  10	  0.0003078358
# 879	    15	        0.04603143	0.5071435	    roc_auc	  hand_till	    0.9987901	  10	  0.0002968329
# 752	    11	        0.03238721	0.8381573	    roc_auc	  hand_till	    0.9987422	  10	  0.0002720549

# obtain mean roc_auc score
tuning_gradient_tree_results %>%
  show_best(metric = "roc_auc") %>%
  group_by(.metric) %>%
  summarize(mean = mean(mean))

# .metric   mean
# roc_auc	0.9988123			

best_tune_tree_model <- tuning_gradient_tree_results %>% 
  select_best(metric = 'roc_auc')

final_tune_tree_workflow <- tree_workflow %>% 
  finalize_workflow(best_tune_tree_model)

final_tune_tree_fit <- final_tune_tree_workflow %>% 
  last_fit(split = syn_df_split, metrics = tree_metrics)

final_tune_tree_fit %>% 
  collect_metrics()

# Tuned Gradient Boost Model Results
  # accuracy	    multiclass	  0.9716981
  # sens	        macro	        0.9704182
  # spec	        macro	        0.9952833
  # roc_auc	      hand_till	    0.9989265
```


# Model 4 - KNN: Real Data (normal_df)

```{r}

#Create Recipe
knn_recipe <- recipe(NObeyesdad ~ ., data = normal_obesity_train) %>%
  step_novel(all_nominal_predictors(), new_level = "other") %>%
  step_dummy(all_nominal_predictors()) %>%
  step_zv(all_predictors()) %>%
  step_normalize(all_numeric_predictors())  

#Structure Model
knn_model <- nearest_neighbor(
  neighbors = tune(),   # this is k
  weight_func = "rectangular",
  dist_power = 2
) %>%
  set_engine("kknn") %>%
  set_mode("classification")

#Build workflow
knn_workflow <- workflow() %>%
  add_recipe(knn_recipe) %>%
  add_model(knn_model)

#Cross validation of k-NN model
#Check for best k-value and prints 20 k-values + accuracy
knn_grid <- tibble(neighbors = 1:20)
knn_tuned <- knn_workflow %>%
  tune_grid(
    resamples = normal_tree_folds,
    grid = knn_grid,
    metrics = tree_metrics
  )

knn_tuned %>%
  collect_metrics() %>%
  filter(.metric == "accuracy") %>%
  select(k = neighbors, accuracy = mean)

# obtain mean roc_auc score
knn_tuned %>%
  show_best(metric = "roc_auc") %>%
  group_by(.metric) %>%
  summarize(mean = mean(mean))

# .metric   mean
# roc_auc   0.6937371	

# Creates plot for k-values vs Accuracy
knn_tuned %>%
  collect_metrics() %>%
  filter(.metric == "accuracy") %>%
  ggplot(aes(neighbors, mean)) +
  geom_line() +
  geom_point() +
  labs(title = "KNN Accuracy vs K", x = "k", y = "Accuracy")

#Finalize k-NN
best_knn <- knn_tuned %>%
  select_best(metric = "accuracy")

final_knn_workflow <- knn_workflow %>%
  finalize_workflow(best_knn)

best_knn

#Test Performance
final_knn_fit <- final_knn_workflow %>%
  last_fit(split = normal_df_split, metrics = tree_metrics)

final_knn_fit %>%
  collect_metrics()

# KNN Results
# accuracy	multiclass	0.5968992
# sens	    macro	      0.2596267
# spec	    macro	      0.8908521		
# roc_auc	  hand_till	  0.6443231

```

# Model 4 - KNN: Synthetic Data (df)

```{r}
#Create Recipe
knn_recipe <- recipe(NObeyesdad ~ ., data = syn_obesity_train) %>%
  step_novel(all_nominal_predictors(), new_level = "other") %>%
  step_dummy(all_nominal_predictors()) %>%
  step_zv(all_predictors()) %>%
  step_normalize(all_numeric_predictors())  

#Structure Model
knn_model <- nearest_neighbor(
  neighbors = tune(),   # this is k
  weight_func = "rectangular",
  dist_power = 2
) %>%
  set_engine("kknn") %>%
  set_mode("classification")

#Build workflow
knn_workflow <- workflow() %>%
  add_recipe(knn_recipe) %>%
  add_model(knn_model)

#Cross validation of k-NN model
#Check for best k-value and prints 20 k-values + accuracy
knn_grid <- tibble(neighbors = 1:20)
knn_tuned <- knn_workflow %>%
  tune_grid(
    resamples = syn_tree_folds,
    grid = knn_grid,
    metrics = tree_metrics
  )

knn_tuned %>%
  collect_metrics() %>%
  filter(.metric == "accuracy") %>%
  select(k = neighbors, accuracy = mean)

# obtain mean roc_auc score
knn_tuned %>%
  show_best(metric = "roc_auc") %>%
  group_by(.metric) %>%
  summarize(mean = mean(mean))

# .metric   mean
# roc_auc	  0.9416791				

# Creates plot for k-values vs Accuracy
knn_tuned %>%
  collect_metrics() %>%
  filter(.metric == "accuracy") %>%
  ggplot(aes(neighbors, mean)) +
  geom_line() +
  geom_point() +
  labs(title = "KNN Accuracy vs K", x = "k", y = "Accuracy")

#Finalize k-NN
best_knn <- knn_tuned %>%
  select_best(metric = "accuracy")

final_knn_workflow <- knn_workflow %>%
  finalize_workflow(best_knn)

best_knn

#Test Performance
final_knn_fit <- final_knn_workflow %>%
  last_fit(split = syn_df_split, metrics = tree_metrics)

final_knn_fit %>%
  collect_metrics()

# KNN Results
# accuracy	multiclass	0.8075472
# sens	    macro	      0.8037989
# spec	    macro	      0.9680202		
# roc_auc	  hand_till	  0.8855494
```
